\bf The forestecology R package for fitting and assessing neighborhood models of the effect of interspecific competition on the growth of trees

### 2021-07-21 paper/paper.Rmd
runs and gives result, but looks funky!

```{r appendix2-code}

mult_dist_comp <- tibble(
  dist = c(2.5, 5, 7.5, 10, 12.5 ),
  rmse = 0
)

@@

  focal_vs_comp_scbi <- growth_scbi %>%
    create_focal_vs_comp(comp_dist, blocks = blocks_scbi, id = "stemID")
  focal_vs_comp_scbi %>% 
    select(focal_ID, focal_sp, geometry, growth, comp)

  focal_vs_comp_scbi <- focal_vs_comp_scbi %>%
    run_cv(comp_dist = mult_dists[i], blocks = blocks_scbi)

>>>>

```{r appendix2-code}
mult_dist_comp <- tibble(
  dist = c(2.5, 5, 7.5, 10, 12.5),
  rmse = 0
)

@@

  focal_vs_comp_scbi <- growth_scbi %>%
    create_focal_vs_comp(comp_dist = comp_dist, blocks = blocks_scbi, id = "stemID")
  focal_vs_comp_scbi %>% 
    select(focal_ID, focal_sp, geometry, growth, comp)

  focal_vs_comp_scbi <- focal_vs_comp_scbi %>%
    run_cv(comp_dist = comp_dist, blocks = blocks_scbi)

### 2021-07-21 paper/paper.tex
runs and gives result, but looks funky!

>>>>

Above we set the cut off distance for two stems to compete at 7.5 m. Our
package can be used to find which distance is best supported by the
data. Here we give an example.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{mult_dist_comp <-}\StringTok{ }\KeywordTok{tibble}\NormalTok{(}
  \DataTypeTok{dist =} \KeywordTok{c}\NormalTok{(}\FloatTok{2.5}\NormalTok{, }\DecValTok{5}\NormalTok{, }\FloatTok{7.5}\NormalTok{, }\DecValTok{10}\NormalTok{, }\FloatTok{12.5}\NormalTok{),}
  \DataTypeTok{rmse =} \DecValTok{0}
\NormalTok{)}

\ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{1}\OperatorTok{:}\KeywordTok{length}\NormalTok{(mult_dist_comp}\OperatorTok{$}\NormalTok{dist))}
\NormalTok{\{}
\NormalTok{  comp_dist <-}\StringTok{ }\NormalTok{mult_dist_comp}\OperatorTok{$}\NormalTok{dist[i]}
\NormalTok{  growth_scbi <-}\StringTok{ }\NormalTok{growth_scbi }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{add_buffer_variable}\NormalTok{(}\DataTypeTok{size =}\NormalTok{ comp_dist, }\DataTypeTok{region =}\NormalTok{ study_region_scbi)}

\NormalTok{  focal_vs_comp_scbi <-}\StringTok{ }\NormalTok{growth_scbi }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{create_focal_vs_comp}\NormalTok{(}\DataTypeTok{comp_dist =}\NormalTok{ comp_dist, }\DataTypeTok{blocks =}\NormalTok{ blocks_scbi, }\DataTypeTok{id =} \StringTok{"stemID"}\NormalTok{)}
\NormalTok{  focal_vs_comp_scbi }\OperatorTok{%>%}\StringTok{ }
\StringTok{    }\KeywordTok{select}\NormalTok{(focal_ID, focal_sp, geometry, growth, comp)}

\NormalTok{  focal_vs_comp_scbi <-}\StringTok{ }\NormalTok{focal_vs_comp_scbi }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{run_cv}\NormalTok{(}\DataTypeTok{comp_dist =}\NormalTok{ comp_dist, }\DataTypeTok{blocks =}\NormalTok{ blocks_scbi)}

\NormalTok{  mult_dist_comp}\OperatorTok{$}\NormalTok{rmse[i] <-}\StringTok{ }\NormalTok{focal_vs_comp_scbi }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{rmse}\NormalTok{(}\DataTypeTok{truth =}\NormalTok{ growth, }\DataTypeTok{estimate =}\NormalTok{ growth_hat) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{pull}\NormalTok{(.estimate)}
\NormalTok{\}}

\NormalTok{mult_dist_comp }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{ggplot}\NormalTok{(}\KeywordTok{aes}\NormalTok{(dist,rmse)) }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_point}\NormalTok{() }\OperatorTok{+}
\StringTok{  }\KeywordTok{xlab}\NormalTok{(}\StringTok{'Distance (m)'}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{ylab}\NormalTok{(}\StringTok{'RMSE (cm)'}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{center}\includegraphics[width=1\linewidth]{Figures/appendix2-code-1} \end{center}
